Estimating epidemiological quantities from repeated cross-sectional prevalence measurements

### 2022-03-06 docs/paper.Rmd
results

```{r params-table}
biol_params %>% 
  kbl(caption = paste0(
    "Estimates and credible intervals (CIs, as quantiles of the posterior",
    "distribution) of biological parameters."
    ), booktabs = TRUE) %>%
  kable_styling()
```

>>>>

```{r params-table}
biol_params %>%
  kbl(caption = paste0(
    "Estimates and credible intervals (CIs, as quantiles of the posterior ",
    "distribution) of biological parameters."
    ), booktabs = TRUE) %>%
  kable_styling()
```
